---
title: "Imputation-RegressionBased"
author: "SP"
date: "14/11/2019"
output: pdf_document
---


```{r}

```



```{r}
ds<-read.csv("fitness.csv")
ds
```

#### RunPulse was read as the factor, so we will convert it into int
```{r}
ds$RunPulse = as.double(ds$RunPulse)
ds
```


### Missing values
#### Oxygen - has complete data
#### RunTime - has three observations missing
#### RunPulse - has three observations (4, 11, 14) missing together with RunTime and five on its own (5, 8, 18,19, 25)


### Implementation of the regression as follows
#### RunTime - on Oxygen to predict missing observations 4, 11, 14
```{r}
RunTime_on_Oxygen<-lm(RunTime~Oxygen,data=ds)
new_ds_1<-data.frame(Oxygen=c(59.571,50.541,47.273))
predict(RunTime_on_Oxygen,new_ds_1)
```

#### RunPulse - on Oxygen to predict missing observations 4, 11, 14
```{r}
RunPulse_on_Oxygen<-lm(RunPulse~Oxygen,data=ds)
predict(RunPulse_on_Oxygen,new_ds_1)
```

#### RunPulse - on Oxygen and RunTime to predict missing observations 5, 8, 18, 19, 25
```{r}
RunPulse_on_Oxygen_RunTime<-lm(RunPulse~RunTime+Oxygen,data=ds)
new_ds_1<-data.frame(Oxygen=c(49.874,49.091,46.672,46.774,45.118),
                     RunTime=c(9.22,10.85,10.00,10.25,11.08))
predict(RunPulse_on_Oxygen_RunTime,new_ds_1)
```

```{r}
new_ds_1
```

