---
title: "VariableSelection-HittersData"
author: "SP"
date: "28/10/2019"
output: pdf_document
---

```{r}
library(car)
library(MASS)
library(LEAP)
library(dplyr)
library(leaps)
library(ISLR)
```

```{r}
ds<-read.csv("Hitters.csv")
head(ds)
```

```{r}
dim(ds)
```

```{r}
names(ds)
```

```{r}
summary(ds)
```

```{r}
ds=na.omit(ds) # removing the NA's of the Salary
dim(ds)
```

```{r}
model1=lm(Salary~., data=ds)
summary(model1)
```

```{r}
#cor(ds)
```






```{r}
AIC(model1)
```

```{r}
BIC(model1)
```

## Let us choose the 7 variables

```{r}
reg_all=regsubsets(Salary~., data=ds, nvmax=7)
```

```{r}
summary(reg_all)
```


```{r}
coef(reg_all, 7)
```

## functions available in regsubset and summary

```{r}
names(reg_all)
```

```{r}
reg_all_summary = summary(reg_all)
```


```{r}
names(reg_all_summary)
```

## Forward Selection with nvmax number of regressors

```{r}
forward_reg = regsubsets(Salary~., data=ds, nvmax= 19,method="forward")
summary(forward_reg)
```

```{r}
names(forward_reg)
```




## Backward Elimination with nvmax number of regressors

```{r}
backward_reg = regsubsets(Salary~., data=ds, nvmax= 19, method="backward")
summary(backward_reg)
```

```{r}
names(backward_reg)
```

## Variable Selection using nvmax=5

```{r}
reg_all_5 = regsubsets(Salary~., data=ds, nvmax=5)
#reg_all_5
```

```{r}
summary_5 = summary(reg_all_5)
summary_5
```

```{r}
bestsubset_5=which.max(summary_5$adjr2)
bestsubset_5
```


```{r}
plot(summary_5$adjr2, xlab="Number of regressors", ylab="adjusted R-square", type ="l", col="red")
points(bestsubset_5,summary_5$adjr2[bestsubset_5],col="blue",pch = 8)
```
From the above curve we can notice that, it is not yet reached the optimum number of regressors


## Variable Selection using nvmax=19

```{r}
reg_all_19=regsubsets(Salary~., data=ds, nvmax=19)
```


```{r}
summary(reg_all_19)
```


```{r}
summary_19 = summary(reg_all_19)
summary_19$adjr2
```


```{r}
bestsubset_19=which.max(summary_19$adjr2)
bestsubset_19
```


## Plots for variable selection


```{r}
plot(reg_all_19, scale="adjr2", col="green")
```

```{r}
plot(summary_19$adjr2, xlab="Number of regressors", ylab="adjusted R-square", type ="l", col="red")
points(bestsubset_19,summary_19$adjr2[bestsubset_19],col="blue",pch = 8)
```


